An indexed construction of semi-simplicial and semi-cubical types

### 2022-05-18 paper/paper.tex
paper, tab-faces: create more key fams; roadblock at nested

% Magic with xkeyval to go over the 9-argument limit of LaTeX
\makeatletter
\define@key{Ex}{D}{#1}
\define@key{Ex}{d}{#1}
\define@key{Ex}{E}{#1}
\define@key{Ex}{l}{#1}
\define@key{Ex}{c}{#1}
\makeatother

% Frame, layer, and filler: the general macro
\makeatletter
\newcommandx{\prim}[6][2=,3=,4=,5=,6=]{\ensuremath{\mathsf{\color{indian-yellow}{#1}}_{#2}^{\joinargs{}[#3][#4][#5]}}\@ifstar{}{\setkeys*{Ex}{#6}}}
\makeatother

% Restriction for frame, layer, and filler: the general macro
\makeatletter
\newcommandx{\restr}[8][2=,3=,4=,5=,6=,7=,8=]{\ensuremath{\mathsf{\color{russian-green}{restr}}_{\mathsf{\color{indian-yellow}{#1}}\joinargs{,}[#2][#3][#4]}^{\joinargs{}[#5][#6][#7]}}\@ifstar{}{\setkeys*{Ex}{#8}}}
\makeatother

@@

% Hack: we'd like \coh to take 10 arguments, with the 10th being passed to
% xkeyval, but this is not possible. The only possible compromise is to join
% #7, and #8 by hand in usage of \coh, by hand.
\makeatletter
\newcommandx{\coh}[9][2=,3=,4=,5=,6=,7=,8=,9=]{\ensuremath{\mathsf{\color{chestnut}{coh}}_{\mathsf{\color{indian-yellow}{#1}}\joinargs{,}[#2][#3][#4][#5][#6]}^{\joinargs{}[#7][#8]}}\@ifstar{}{\setkeys*{Ex}{#9}}}
\makeatother

@@

% Coherence conditions for frame, layer, and filler
\renewcommandx{\cohf}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{cohframe}[#1][#2][#3][#4][#5][#6,#7][#8][#9]}
\renewcommandx{\cohl}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{cohlayer}[#1][#2][#3][#4][#5][#6,#7][#8][#9]}
\renewcommandx{\cohc}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{cohfiller}[#1][#2][#3][#4][#5][#6,#7][#8][#9]}

>>>>

% Magic with xkeyval to go over the 9-argument limit of LaTeX
\makeatletter
\define@cmdkey{prim-frame}{D}{#1}
\define@cmdkey{prim-layer}{D}{#1}
\define@cmdkey{prim-layer}{d}{#1}
\define@cmdkey{prim-filler}{D}{#1}
\define@cmdkey{prim-filler}{E}{#1}
\define@cmdkey{prim-filler}{d}{#1}

\define@cmdkey{restr-frame}{D}{#1}
\define@cmdkey{restr-frame}{d}{#1}
\define@cmdkey{restr-layer}{D}{#1}
\define@cmdkey{restr-layer}{d}{#1}
\define@cmdkey{restr-layer}{l}{#1}
\define@cmdkey{restr-filler}{D}{#1}
\define@cmdkey{restr-filler}{E}{#1}
\define@cmdkey{restr-filler}{d}{#1}
\define@cmdkey{restr-filler}{c}{#1}

\define@cmdkey{coh-frame}{D}{#1}
\define@cmdkey{coh-frame}{d}{#1}
\define@cmdkey{coh-layer}{D}{#1}
\define@cmdkey{coh-layer}{d}{#1}
\define@cmdkey{coh-layer}{l}{#1}
\define@cmdkey{coh-filler}{D}{#1}
\define@cmdkey{coh-filler}{E}{#1}
\define@cmdkey{coh-filler}{d}{#1}
\define@cmdkey{coh-filler}{c}{#1}
\makeatother

% Frame, layer, and filler: the general macro
\makeatletter
\newcommandx{\prim}[6][2=,3=,4=,5=,6=]{\ensuremath{\mathsf{\color{indian-yellow}{#1}}_{#2}^{\joinargs{}[#3][#4][#5]}}\@ifstar{}{\setkeys*{prim-#1}{#6}}}
\makeatother

% Restriction for frame, layer, and filler: the general macro
\makeatletter
\newcommandx{\restr}[8][2=,3=,4=,5=,6=,7=,8=]{\ensuremath{\mathsf{\color{russian-green}{restr}}_{\mathsf{\color{indian-yellow}{#1}}\joinargs{,}[#2][#3][#4]}^{\joinargs{}[#5][#6][#7]}}\@ifstar{}{\setkeys*{restr-#1}{#8}}}
\makeatother

@@

% Hack: we'd like \coh to take 10 arguments, with the 10th being passed to
% xkeyval, but this is not possible. The only possible compromise is to join
% #7, and #8 by hand in usage of \coh, by hand.
\makeatletter
\newcommandx{\coh}[9][2=,3=,4=,5=,6=,7=,8=,9=]{\ensuremath{\mathsf{\color{chestnut}{coh}}_{\mathsf{\color{indian-yellow}{#1}}\joinargs{,}[#2][#3][#4][#5][#6]}^{\joinargs{}[#7][#8]}}\@ifstar{}{\setkeys*{coh-#1}{#9}}}
\makeatother

@@

% Coherence conditions for frame, layer, and filler
\renewcommandx{\cohf}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{frame}[#1][#2][#3][#4][#5][#6,#7][#8][#9]}
\renewcommandx{\cohl}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{layer}[#1][#2][#3][#4][#5][#6,#7][#8][#9]}
\renewcommandx{\cohc}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{filler}[#1][#2][#3][#4][#5][#6,#7][#8][#9]}
